---
title: "MDMA amygdala baseline stratification"
author: "Xue Zhang"
date: "10/25/2024"
output:
  html_document: default
  pdf_document: default
  word_document: default
always_allow_html: yes
---


### load envionment and packages and subfunctions
```{r setup, include=FALSE}
# load all related packages
pacman::p_load(pacman,here,knitr, rio, ggplot2, lme4, tidyverse, sjPlot, performance, see, broom.mixed, kableExtra, janitor, ggeffects, dplyr, gridExtra, qqplotr, emmeans, pbkrtest, knitr,ggpubr, here, table1, psych, broom,lsr, rstatix, formatR, RVAideMemoire, labelled, cowplot, readr, svglite, rmcorr, cowplot, grid, gtable, RColorBrewer, extrafont, corrplot, grDevices,icesTAF, gganimate, mice) 

# load global options
opts_chunk$set(echo = TRUE)

# kable output
options(kableExtra.auto_format = FALSE)

# set up the contrast option for ANOVA
options(contrasts = c("contr.sum","contr.poly"))

# load functions for data manipulations
#source(here('R', 'data_manipulation.R'))

# load functions for data visualization
add_theme <- function(myplot, xtitle_size, title_size, legend_title_size)
{
  myplot <- myplot + theme(axis.line = element_line(colour = 'black', size = 0.1),
                           axis.ticks.length = unit(0.05, "cm"),
                           axis.ticks = element_line(colour = "black", size = 0.1),
                           axis.title.x = element_blank(),
                           # axis.title.x = element_text(colour = "black",size = xtitle_size, family = "Arial"),
                           plot.title = element_text(hjust=0.5, size = title_size, family = "Arial", face="bold", margin=margin(b = 0.01, unit = "inch")),
                           axis.text.x = element_text(colour = "black",size = xtitle_size, family = "Arial"),
                           axis.title.y=element_blank(),
                           axis.text.y = element_text(colour = "black",size = title_size-1, family = "Arial"),
                           strip.text.x = element_text(size = xtitle_size, colour = "black", family = "Arial"), strip.background = element_blank(),
                           legend.text = element_text(size=legend_title_size, family = "Arial"),
                           legend.background = element_rect(fill = "transparent"),
                           panel.background = element_rect(fill = "transparent"),
                           legend.title = element_text(size=legend_title_size, family = "Arial"))
}

# create folder, can work even if parent folder doesn't exist
create_folder_subfolder <- function(folder)
{
  dir.create(folder, recursive = TRUE)
  
}
```


### Define Data Directory and Create Folders for Output Figures
```{r define_folders}

# Data folder path
data_dir <- "/Users/xuezhang/Documents/Stanford/Projects/P50/Analysis/CSV"
code_dir <- "/Users/xuezhang/Documents/Stanford/Projects/P50/Analysis/Scripts/R/P50_visualization_analysis"

# Define and create figure directories
figure_dir <- file.path(code_dir, "Figures_MDMA_amyg_stratification_PAPER")
figure_subdirs <- c("TIFF", "PDF")
figure_categories <- c("Boxplot")

# Create subfolders within each main figure subdirectory
for (subdir in figure_subdirs) {
  for (category in figure_categories) {
    target_dir <- file.path(figure_dir, subdir, category)
    create_folder_subfolder(target_dir)
  }
}

```

### Define Parameters for Subjects, Dosage, and Plotting
```{r define_parameters}
# Subject information
num_subjects <- 17  # Total number of subjects
subject_list <- as.character(1:num_subjects)
subject_labels <- 1:num_subjects

# Dosage levels
dosage_4sessions <- c("Baseline", "Placebo", "80mg", "120mg")
dosage_3sessions <- c("Placebo", "80mg", "120mg")

# Load and clean dosage data
dosage_data <- import(file.path(data_dir, "MDMA_Dose_info_unblinded_10072021.xlsx")) %>%
  select(-c("...6", "...7", "...8", "...9")) %>%
  rename(s0 = "s00", s1 = "s01", s2 = "s02", s3 = "s03", Subjects = "ID") %>%
  pivot_longer(-Subjects, names_to = "Visit", values_to = "Dosage") %>%
  mutate(Dosage = gsub("baseline", "Baseline", Dosage),
         Dosage = factor(Dosage, levels = dosage_4sessions)) %>%
  filter(as.numeric(Subjects) <= num_subjects) %>%
  mutate(Subjects = factor(Subjects, levels = subject_list)) %>%
  arrange(as.numeric(Subjects)) %>%
  filter(Subjects != 4)

xtitle_size <- 4
title_size <- 7
legend_title_size <- 9
x_label_size <- 7

```



# read redcap questionnaire, brain data, and webneuro data
```{r read data}
source(file.path(code_dir, 'R', 'MDMA_read_redcap_data_forupload.R'))
source(file.path(code_dir, 'R', 'MDMA_read_biotype_forupload.R'))
source(file.path(code_dir, 'R', 'MDMA_read_webneuro_data_forupload.R'))
```

### Stratify Subjects by Baseline Amygdala Activation - Median Split
### Fig. 2b
```{r fig.width=2,fig.height=2, fig.align='center',comment= NA, message=FALSE, tidy = TRUE, results='asis',warning=FALSE}
# Read baseline amygdala activation data
biotype_baseline <- biotype_all %>%
  drop_na() %>%
  filter(Dosage == 'Baseline') %>%
  select(-Dosage) %>%
  mutate(`act-nonconscious-threat_vs_neutral_Amygdala` = 
           (`act-nonconscious-threat_vs_neutral-779062_Left_Amygdala` + 
            `act-nonconscious-threat_vs_neutral-176064_Right_Amygdala`) / 2)

# Define groups based on baseline amygdala activation
variable <- 'act-nonconscious-threat_vs_neutral_Amygdala'
group_df_all <- biotype_baseline %>%
  pivot_longer(-Subjects, names_to = 'variables', values_to = 'value') %>%
  filter(variables == variable) %>%
  mutate(Group = ifelse(value >= median(value), 'high', 'low')) %>%
  select(Subjects, Group, value, variables)

# Clean the group variable for analysis
group_df <- group_df_all %>%
  filter(variables == variable) %>%
  select(-value, -variables)

# Save raw activation values as well
values_dfs <- group_df_all %>%
select(-Group) %>%
pivot_wider(names_from = variables, values_from = value)

# Check sample size and group statistics of amygdala activation
summary_group_value <- group_df_all %>%
  filter(variables == variable) %>%
  group_by(Group) %>%
  summarise(
    avg = mean(value, na.rm = TRUE),
    sd = sd(value, na.rm = TRUE),
    n = n(),
    se = sd / sqrt(n)
  ) %>%
  rename(value = avg) %>%
  ungroup()

# Plot baseline amygdala activation for high and low activation group: mean +/- se and scatter plot
pd <- position_jitter(width = 0.1)
colors_high_low <- c("#FF3705", "#F4B183")
xlabel_text <- c("high", "low")

ylim_max <- max(summary_group_value$value) + 1.1 * max(summary_group_value$se)
ylim_min <- min(summary_group_value$value) - 1.1 * max(summary_group_value$se)

# Create the ggplot with data points, error bars, and theme adjustments
pd <- position_dodge(0.2)
myplot <- summary_group_value %>%
  ggplot(aes(x = Group, y = value)) +
  geom_point(
    aes(group = Group, color = Group),
    position = pd,
    data = group_df_all,
    alpha = 0.5,
    size = 0.2,
    stroke = 0.3
  ) +
  geom_point(
    aes(color = Group),
    alpha = 1,
    size = 1,
    position = pd
  ) +
  geom_errorbar(
    aes(color = Group, ymin = value - se, ymax = value + se),
    width = 0,
    size = 0.25,
    position = pd
  ) +
  scale_colour_manual(values = colors_high_low) +
  scale_fill_manual(values = colors_high_low) +
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  theme_classic() +
  scale_x_discrete(breaks = waiver(), labels = xlabel_text) +
  scale_y_continuous(
    name = "",
    limits = c(-2, 2),
    breaks = c(-2, -1, 0, 1, 2),
    expand = c(0, 0)
  ) +
  guides(
    color = guide_legend(override.aes = list(alpha = 0.5)),
    col = guide_legend(nrow = 1)
  ) +
  geom_hline(yintercept = 0, size = 0.1, linetype = "dashed", color = "grey") +
  theme(legend.position = "off")

# Apply additional theme settings
myplot <- add_theme(myplot, xtitle_size, title_size, legend_title_size)


# Save the plot as TIFF and PDF
figure_width <- 0.8
ggsave(filename = file.path(figure_dir, "TIFF/Boxplot/Baseline_PredictDrug_Experience", paste0(variable, "_Baseline_stratification_11042024.TIFF")),
       plot = myplot, width = figure_width, height = 1, dpi = 1000)

ggsave(filename = file.path(figure_dir, "PDF/Boxplot/Baseline_PredictDrug_Experience", paste0(variable, "_Baseline_stratification_11042024.PDF")),
       device = cairo_pdf, plot = myplot, width = figure_width, height = 1, dpi = 300)
myplot
```


### Read baseline demographics and symptoms, and report statistics by comparing high and low groups: 
### Table 1
```{r fig.width=12,fig.height=6, comment= NA, message=FALSE, tidy = TRUE}
# Extract and clean demographic data
demo_graphic <- questionnaire_data %>%
  filter(Visit %in% c('screening', 's0')) %>%
  select(
    Subjects, Visit, redcap_repeat_instance, Age, Gender, 
    educationscreen___1, educationscreen___2, educationscreen___3, 
    educationscreen___4, educationscreen___5, educationscreen___6, 
    ehi_handedness, Race, PHQ9, GAD7, pclc_total, ELS) %>%
  group_by(Subjects) %>%
  summarise_all(~ first(na.omit(.))) %>%
  filter(Visit == 's0') %>%
  select(-redcap_repeat_instance, -Visit)

# Create education level variable
education <- demo_graphic %>%
  select(
    Subjects, educationscreen___1, educationscreen___2, 
    educationscreen___3, educationscreen___4, educationscreen___5, 
    educationscreen___6
  ) %>%
  mutate(
    Education = case_when(
      educationscreen___6 == 1 ~ 6,
      educationscreen___5 == 1 ~ 5,
      educationscreen___4 == 1 ~ 4,
      educationscreen___3 == 1 ~ 3,
      educationscreen___2 == 1 ~ 2,
      educationscreen___1 == 1 ~ 1,
      TRUE ~ NA_real_
    )
  ) %>%
  select(Subjects, Education)

# Merge demographic data with group data and education levels
demo_graphic <- Reduce(function(x, y) merge(x, y, by = "Subjects", all = TRUE), list(group_df, demo_graphic, education)) %>%
  filter(!is.na(Group))

# Prepare and reformat data for Table 1
demo_graphic_table <- demo_graphic %>%
  mutate(
    Gender = factor(Gender, levels = c(0, 1), labels = c("Male", "Female")),
    ehi_handedness = factor(ehi_handedness, levels = c(1, 2, 3), labels = c("Right", "Left", "Ambidextrous")),
    Education = factor(Education, levels = 1:6, labels = c(
      "Less than high school", "Completed high school", 
      "Some college", "Two-year college", "4-year college", 
      "More than 4-year college"
    )),
    Race = factor(Race, levels = 0:6, labels = c(
      "American Indian/Alaska Native", "Asian", 
      "Native Hawaiian or Other Pacific Islander", 
      "Black or African American", "White", 
      "More Than One Race", "Unknown / Not Reported"
    ))
  ) %>%
  set_variable_labels(
    PHQ9 = "9-item Patient Health Questionnaire", 
    GAD7 = "7-Item Generalised Anxiety Disorder", 
    ehi_handedness = "Handedness", 
    ELS = "Early Life Stress Questionnaire",
    pclc_total = "PTSD Checklist-Civilian Version"
  )

# Export the demographic data
demo_graphic_table %>%
  export(file = file.path(data_dir, "Demographic_Characterization_11042024.csv"))

# Set units for Age
units(demo_graphic_table$Age) <- "years"

# Create baseline demographics table with p-values, running t test for continous variables and chisq test for categorical variables
pvalue <- function(x, ...) {
  y <- unlist(x)
  g <- factor(rep(1:length(x), times = sapply(x, length)))
  if (is.numeric(y)) {
    p <- t.test(y ~ g)$p.value
  } else {
    contingency_table <- table(y, g)
    contingency_table <- contingency_table[rowSums(contingency_table) > 0, ]
    if (nrow(contingency_table) >= 2) {
      p <- chisq.test(contingency_table)$p.value
    } else {
      p <- NA
    }
  }
  c("", sub("<", "&lt;", format.pval(p, digits = 3, eps = 0.001)))
}

# Display table with high and low subgoups only, and report p-values comparing high vs low group
table1(
  ~ Age + Gender + Education + ehi_handedness + Race + PHQ9 + GAD7 + pclc_total + ELS | Group, 
  data = demo_graphic_table, 
  overall = FALSE, 
  extra.col = list(`P-value` = pvalue)
)

# Display table with total sample alongside high and low subgroups
table1(
  ~ Age + Gender + Education + ehi_handedness + Race + PHQ9 + GAD7 + pclc_total + ELS | Group, 
  data = demo_graphic_table, overall=c(left="Total"))

```



### Compare additional baseline behavioral and symptoms characteristics of high vs low groups and create visuals: 
### Fig. 2c and Suppl. Fig 1a-1d
```{r fig.width=2, fig.height=2, fig.align='center', comment=NA, message=FALSE, tidy=TRUE, results='asis', warning=FALSE}

# Select behavioral and symptoms data and merge into non_brain_data_baseline
webneuro_baseline <- webneuro_baseline %>%
  select(Subjects, dgttrtAvN_norm)

non_brain_data_baseline <- Reduce(function(x, y) merge(x, y, by = "Subjects", all=TRUE), list(webneuro_baseline, questionnaire_baseline)) %>%
  arrange(Subjects)

# Add group information
non_brain_data_baseline_group <- Reduce(function(x, y) merge(x, y, by = "Subjects", all=TRUE), list(group_df, non_brain_data_baseline, values_dfs))

# Reshape data for analysis
non_brain_data_baseline_long <- non_brain_data_baseline_group %>%
  pivot_longer(-c(Subjects, Group, Age, Gender), names_to = 'variables', values_to = 'value') %>%
  drop_na() %>%
  filter(grepl('GAD7|PHQ9|dgttrtAvN_norm|pcl|ELS|nonconscious', variables))

# Conduct independent t-tests between high vs low groups
ttest_table <- non_brain_data_baseline_long %>%
  group_by(variables) %>%
  t_test(value ~ Group, conf.level = 0.95, var.equal = TRUE, detailed = TRUE) %>%
  add_significance(p.col="p", output.col="p.signif") %>%
  arrange(variables) %>%
  kbl(caption = "Baseline characteristics of high vs low reactivity groups: t-test") %>%
  kable_classic(full_width = FALSE, html_font = "Arial", font_size = 10)

ttest_table

# Calculate effect size (Cohen's d) for each comparison
cohen_table <- non_brain_data_baseline_long %>%
  group_by(variables) %>%
  cohens_d(value ~ Group, var.equal = TRUE, paired = FALSE) %>%
  arrange(variables) %>%
  kbl(caption = "Baseline characteristics of high vs low reactivity groups: effect size") %>%
  kable_classic(full_width = FALSE, html_font = "Arial", font_size = 10)

cohen_table

# Plotting for each selected measure
Selected_measure <- unique(non_brain_data_baseline_long$variables)
plot_titles <- Selected_measure
myplot_all <- list()
xtitle_size <- 5
title_size <- 6
legend_title_size <- 3
colors_high_low <- c("#FF3705", "#F4B183")
xlabel_text <- c("high", "low")

# Iterate over each selected measure for plotting
for (imeasure in seq_along(Selected_measure)) {
  
  # Data for the current measure
  data_fortest <- non_brain_data_baseline_long %>%
    filter(variables == Selected_measure[imeasure]) %>%
    drop_na()

  # Summary statistics for the current measure
  data_fortest_summary <- data_fortest %>%
    group_by(Group) %>%
    summarize(avg = mean(value), sd = sd(value), n = n(), se = sd / sqrt(n)) %>%
    rename(value = avg) %>%
    ungroup()
  
  # Set y-axis limits
  ylim_max <- max(data_fortest_summary$value) + 1.1 * max(data_fortest_summary$se)
  ylim_min <- min(data_fortest_summary$value) - 1.1 * max(data_fortest_summary$se)

  # Plot for each measure
  myplot <- ggplot(data_fortest_summary, aes(x = Group, y = value)) +
    geom_point(aes(group = Group, color = Group), position = pd, data = data_fortest, alpha= 0.5, size = 0.2) +
    geom_point(aes(color = Group), alpha = 1, size = 1, position = position_dodge(0.2)) +
    geom_errorbar(aes(color = Group, ymin = value - se, ymax = value + se), width = 0, size = 0.25) +
    scale_colour_manual(values = colors_high_low) +
    theme_classic() + 
    scale_x_discrete(labels = xlabel_text) +
    scale_colour_manual(values = colors_high_low) +
    theme(legend.position = "off") +
    labs(y = plot_titles[imeasure])

  # Conditional settings for the specific variable
  if (plot_titles[imeasure] == 'dgttrtAvN_norm') {
    myplot <- myplot +
      geom_hline(yintercept = 0, size = 0.1, linetype = "dashed", color = "grey") +
      scale_y_continuous(name = "", limits = c(-2, 2), breaks = c(-2, -1, 0, 1, 2), expand = c(0, 0)) +
      scale_y_reverse()
  }
  print(myplot)
  
  # Save each plot
  figure_width <- 0.8
  ggsave(filename = file.path(figure_dir, "TIFF/Boxplot/Baseline_PredictDrug_Experience/Baseline", paste0(plot_titles[imeasure], "_bygroup_11042024.TIFF")), 
         plot = myplot, width = figure_width, height = 1, dpi = 1000)
  ggsave(filename = file.path(figure_dir, "PDF/Boxplot/Baseline_PredictDrug_Experience/Baseline", paste0(plot_titles[imeasure], "_bygroup_11042024.pdf")), 
         device = cairo_pdf, plot = myplot, width = figure_width, height = 1, dpi = 300)
}
```



### Compare MDMA-Induced Acute Effects Between High vs. Low Group under Placebo and 120mg MDMA, and creat visuals:
### Fig. 3a-3h and Suppl. Fig. 2a-2h, Suppl. Table 1
```{r fig.width=2,fig.height=2, fig.align='center',comment= NA, message=FALSE, tidy = TRUE, results='asis',warning=FALSE}
# Define outcomes to be tested
brain_variable <- biotype_all %>%
  mutate(`act-nonconscious-threat_vs_neutral_Amygdala` = 
           (`act-nonconscious-threat_vs_neutral-779062_Left_Amygdala` + 
            `act-nonconscious-threat_vs_neutral-176064_Right_Amygdala`) / 2) %>%
  select(Subjects, Dosage, 
         "act-nonconscious-threat_vs_neutral-176064_Right_Amygdala",
         "act-nonconscious-threat_vs_neutral-779062_Left_Amygdala",
         "act-nonconscious-threat_vs_neutral-911981_Right_sgACC",
         "ppi-nonconscious-threat_vs_neutral-911981_Right_sgACC-176064_Right_Amygdala",
         "ppi-nonconscious-threat_vs_neutral-911981_Right_sgACC-779062_Left_Amygdala",
         nonconscious_discarded_percent)

# Select webneuro and questionnaire variables
webneuro_variable <- webneuro_data_4session %>%
  filter(Dosage != "Baseline") %>%
  select(Subjects, Dosage, dgttrtAvN_norm)

variables_select <- colnames(data_repeated_post_pre)[grepl('_post_pre', colnames(data_repeated_post_pre))]

# Define VAS, DASC, and face likability measures
vas_variable <- data_repeated_post_pre %>%
  select(Subjects, Dosage, all_of(variables_select))

dasc_variable <- data_once_pervisit_post_pre %>%
  select(Subjects, Dosage, contains('dasc'))

face_likability <- data_once_pervisit_post_pre %>%
  select(Subjects, Dosage, contains('faces'))

# Covariates (demographics)
demo_covariate <- demo_graphic %>%
  select(Subjects, Age, Gender)

# Merge all outcome variables
outcome <- Reduce(function(x, y) merge(x, y, by = c("Subjects", "Dosage"), all=TRUE), 
                  list(brain_variable, webneuro_variable, dasc_variable, vas_variable, face_likability)) %>%
  arrange(Subjects)

# Merge outcomes with group and demographic information
outcome_withgroup <- Reduce(function(x, y) merge(x, y, by = "Subjects", all = TRUE),
                            list(group_df, demo_covariate, outcome)) %>%
  arrange(Subjects) %>%
  mutate(
    Dosage = factor(Dosage, levels = dosage_3sessions),
    Gender = as.factor(Gender)
  ) %>%
  drop_na(Dosage)

# Check number of subjects in each group with Placebo and 120mg MDMA
test_data <- outcome_withgroup %>%
  filter(Dosage != '80mg') %>%
  group_by(Subjects) %>%
  summarise(N = n(), Group = unique(Group)) %>%
  unique()

test_data

# Reshape data for analysis
outcome_withgroup_longer <- outcome_withgroup %>%
  pivot_longer(cols = -c(Subjects, Group, Age, Gender, Dosage, nonconscious_discarded_percent), names_to = 'variables', values_to = 'value') %>%
  filter(grepl('nonconscious|Amyg|dgttrt|vas_|dasc|face', variables)) %>%
  filter(Dosage != '80mg') %>%
  drop_na()

# Merge baseline amygdala values with outcome data
outcome_withgroup_longer <- merge(values_dfs, outcome_withgroup_longer, by = "Subjects", all=TRUE)

# Define variables of interest and create formula for mixed model analysis
variable_interest <- unique(outcome_withgroup_longer$variables)[-5] # Exclude left amygdala as per your notes
formula <- as.formula("value ~ Dosage*Group + Age + Gender + nonconscious_discarded_percent + (1|Subjects)")

# Run ANOVA on each variable to assess Dosage*Group interaction
anova_table <- outcome_withgroup_longer %>%
  filter(variables %in% variable_interest) %>%
  split(.$variables) %>%
  map(~anova(lmer(formula, data = ., REML = FALSE), type = 'marginal')) %>%
  tibble(
    dvsub = names(.),
    untidied = .
  ) %>%
  mutate(tidy = map(untidied, broom::tidy)) %>%
  unnest(tidy) %>%
  select(-untidied) %>%
  add_significance() %>%
  filter(term == 'Dosage:Group')

# Display ANOVA results
anova_table %>% 
  kbl(caption = "ANOVA Marginal") %>%
  kable_classic(full_width = F, html_font = "Arial", font_size = 10)

# Fit LMM and perform pairwise comparisons for each variable
results_list <- list()
for (variable in variable_interest) {
  
  data_subset <- outcome_withgroup_longer %>% filter(variables == variable)
  
  # Fit linear mixed model
  lmm <- lmer(formula, data = data_subset, REML = FALSE)
  
  # Calculate estimated marginal means and pairwise comparisons
  emmeans_res <- emmeans(lmm, pairwise ~ Dosage | Group, adjust = "tukey")
  
  # Combine emmeans results with confidence intervals
  emmeans_combined <- summary(emmeans_res$contrasts) %>%
    left_join(confint(emmeans_res$contrasts) %>% 
                select(contrast, Group, lower.CL, upper.CL), by = c("contrast", "Group")) %>%
    mutate(`95% CI` = paste0("[", round(lower.CL, 2), ", ", round(upper.CL, 2), "]")) %>%
    select(-lower.CL, -upper.CL) %>%
    mutate(across(where(is.numeric), round, 2))
  
  results_list[[variable]] <- emmeans_combined
}

# Display pairwise comparison results
final_results <- bind_rows(results_list, .id = "variable")
final_results %>%
  kbl(caption = "Post-hoc Beta Estimates") %>%
  kable_classic(full_width = F, html_font = "Arial", font_size = 10)


# Plotting MDMA-induced effects across placebo and 120mg conditions
Selected_measure <- unique(outcome_withgroup_longer$variables)[-5]
new_names <- c("act-noncon-threat_vs_neutral-R_Amy", "act-noncon-threat_vs_neutral-L_Amy", 
               "act-noncon-threat_vs_neutral-R_sgACC", "ppi-noncon-threat_vs_neutral-R_sgACC-R_Amy", 
               "dgttrtAvN_norm", "dascscore_impair", "dascscore_anxiety", "vas_bewithothers_post_pre",
               "vas_secure_post_pre", "faces1_4" )
xlabel_text <- c("pbo", "120")
myplot_all <- NULL
pd <- position_dodge(0.25)

for (i in seq_along(Selected_measure)) {
  
  data_fortest <- outcome_withgroup_longer %>%
    filter(variables == Selected_measure[i]) %>%
    na.omit()
  
  # Summary stats for plotting
  data_fortest_summary <- data_fortest %>%
    group_by(Group, Dosage) %>%
    summarise(avg = mean(value), sd = sd(value), n = n(), se = sd / sqrt(n)) %>%
    ungroup()
  
  # Generate plot for each measure
  myplot <- data_fortest_summary %>%
    ggplot(aes(x = Dosage, y = avg)) +
    geom_point(aes(color = Group), alpha = 1, size = 1) +
    geom_line(aes(group = Group, color = Group), size = 0.25, alpha = 0.5) +
    geom_errorbar(aes(ymin = avg - se, ymax = avg + se, color = Group), width = 0, size = 0.25) +
    scale_colour_manual(values = colors_high_low) +
    theme_classic() +
    ylab(new_names[i]) +
    scale_x_discrete(labels = xlabel_text) +
    theme(legend.position = "off")
  
  myplot <- add_theme(myplot, xtitle_size, title_size, legend_title_size)
  myplot_all[[i]] <- myplot
}

# Save plots as TIFF and PDF
aligned <- cowplot::align_plots(myplot_all[[1]], myplot_all[[2]], myplot_all[[3]], 
                                myplot_all[[4]], myplot_all[[5]], myplot_all[[6]], 
                                myplot_all[[7]], myplot_all[[8]], myplot_all[[9]], 
                                myplot_all[[10]], align = "hv", axis = "tblr", greedy = TRUE)

for (i in seq_along(Selected_measure)) {
  myplot <- aligned[[i]]
  figure_width <- 0.9
  ggsave(filename = file.path(figure_dir, "TIFF/Boxplot/Baseline_PredictDrug_Experience/Outcome", 
                              paste0(new_names[i], "_bygroupdose_", Sys.Date(), ".TIFF")), 
         plot = myplot, width = figure_width, height = 1, dpi = 1000)
  ggsave(filename = file.path(figure_dir, "PDF/Boxplot/Baseline_PredictDrug_Experience/Outcome", 
                              paste0(new_names[i], "_bygroup_", Sys.Date(), ".pdf")), 
         device = cairo_pdf, plot = myplot, width = figure_width, height = 1, dpi = 300)
}





# Plotting MDMA-induced effects across placebo 80mg MDMA, and 120mg conditions
# Reshape data for analysis
outcome_withgroup_longer <- outcome_withgroup %>%
  pivot_longer(cols = -c(Subjects, Group, Age, Gender, Dosage, nonconscious_discarded_percent), names_to = 'variables', values_to = 'value') %>%
  filter(grepl('nonconscious|Amyg|dgttrt|vas_|dasc|face', variables)) %>%
  drop_na()

# Merge baseline amygdala values with outcome data
outcome_withgroup_longer <- merge(values_dfs, outcome_withgroup_longer, by = "Subjects", all=TRUE)


# Plotting MDMA-induced effects across placebo and 120mg conditions
Selected_measure <- unique(outcome_withgroup_longer$variables)[-5]
new_names <- c("act-noncon-threat_vs_neutral-R_Amy", "act-noncon-threat_vs_neutral-L_Amy", 
               "act-noncon-threat_vs_neutral-R_sgACC", "ppi-noncon-threat_vs_neutral-R_sgACC-R_Amy", 
               "dgttrtAvN_norm", "dascscore_impair", "dascscore_anxiety", "vas_bewithothers_post_pre",
               "vas_secure_post_pre", "faces1_4" )
xlabel_text <- c("pbo", "80", "120")
myplot_all <- NULL
pd <- position_dodge(0.25)

for (i in seq_along(Selected_measure)) {
  
  data_fortest <- outcome_withgroup_longer %>%
    filter(variables == Selected_measure[i]) %>%
    na.omit()
  
  # Summary stats for plotting
  data_fortest_summary <- data_fortest %>%
    group_by(Group, Dosage) %>%
    summarise(avg = mean(value), sd = sd(value), n = n(), se = sd / sqrt(n)) %>%
    ungroup()
  
  # Generate plot for each measure
  myplot <- data_fortest_summary %>%
    ggplot(aes(x = Dosage, y = avg)) +
    geom_point(aes(color = Group), alpha = 1, size = 1) +
    geom_line(aes(group = Group, color = Group), size = 0.25, alpha = 0.5) +
    geom_errorbar(aes(ymin = avg - se, ymax = avg + se, color = Group), width = 0, size = 0.25) +
    scale_colour_manual(values = colors_high_low) +
    theme_classic() +
    ylab(new_names[i]) +
    scale_x_discrete(labels = xlabel_text) +
    theme(legend.position = "off")
  
  myplot <- add_theme(myplot, xtitle_size, title_size, legend_title_size)
  myplot_all[[i]] <- myplot
}

# Save plots as TIFF and PDF
aligned <- cowplot::align_plots(myplot_all[[1]], myplot_all[[2]], myplot_all[[3]], 
                                myplot_all[[4]], myplot_all[[5]], myplot_all[[6]], 
                                myplot_all[[7]], myplot_all[[8]], myplot_all[[9]], 
                                myplot_all[[10]], align = "hv", axis = "tblr", greedy = TRUE)

for (i in seq_along(Selected_measure)) {
  myplot <- aligned[[i]]
  figure_width <- 0.9
  ggsave(filename = file.path(figure_dir, "TIFF/Boxplot/Baseline_PredictDrug_Experience/Outcome", 
                              paste0(new_names[i], "_bygroupdose_alldrugc_", Sys.Date(), ".TIFF")), 
         plot = myplot, width = figure_width, height = 1, dpi = 1000)
  ggsave(filename = file.path(figure_dir, "PDF/Boxplot/Baseline_PredictDrug_Experience/Outcome", 
                              paste0(new_names[i], "_bygroup_alldrugc_", Sys.Date(), ".pdf")), 
         device = cairo_pdf, plot = myplot, width = figure_width, height = 1, dpi = 300)
}


```

### Compare MDMA-Induced Effects Between High vs Low Group - Multiple Imputation Analysis:
### Suppl. Table 2 and 3
```{r fig.width=2,fig.height=2, fig.align='center',comment= NA, message=FALSE, tidy = TRUE, results='asis',warning=FALSE}
# Step 1: Define outcomes to be tested (based on non-imputed code above)
brain_variable <- biotype_all %>%
  mutate(`act-nonconscious-threat_vs_neutral_Amygdala` = 
           (`act-nonconscious-threat_vs_neutral-779062_Left_Amygdala` + 
            `act-nonconscious-threat_vs_neutral-176064_Right_Amygdala`) / 2) %>%
  select(Subjects, Dosage, 
         "act-nonconscious-threat_vs_neutral-176064_Right_Amygdala",
         "act-nonconscious-threat_vs_neutral-779062_Left_Amygdala",
         "act-nonconscious-threat_vs_neutral-911981_Right_sgACC",
         "ppi-nonconscious-threat_vs_neutral-911981_Right_sgACC-176064_Right_Amygdala",
         "ppi-nonconscious-threat_vs_neutral-911981_Right_sgACC-779062_Left_Amygdala",
         nonconscious_discarded_percent)

# Select webneuro and questionnaire variables
webneuro_variable <- webneuro_data_4session %>%
  filter(Dosage != "Baseline") %>%
  select(Subjects, Dosage, dgttrtAvN_norm)

# Define VAS, DASC, and face likability measures
variables_select <- colnames(data_repeated_post_pre)[grepl('_post_pre', colnames(data_repeated_post_pre))]

vas_variable <- data_repeated_post_pre %>%
  select(Subjects, Dosage, all_of(variables_select))

dasc_variable <- data_once_pervisit_post_pre %>%
  select(Subjects, Dosage, contains('dasc'))

face_likability <- data_once_pervisit_post_pre %>%
  select(Subjects, Dosage, contains('faces'))

# Covariates (demographics)
demo_covariate <- demo_graphic %>%
  select(Subjects, Age, Gender)

# Step 2: Combine all outcome variables (similar to non-imputed data approach)
outcome <- Reduce(function(x, y) merge(x, y, by = c("Subjects", "Dosage"), all=TRUE), 
                  list(brain_variable, webneuro_variable, dasc_variable, vas_variable, face_likability)) %>%
    mutate(Dosage = recode(Dosage, "80mg" = "MDose", "120mg" = "HDose")) %>%
  arrange(Subjects) %>%
  mutate(Subjects = as.factor(Subjects))

# Merge outcomes with group and demographic information
outcome_withgroup <- Reduce(function(x, y) merge(x, y, by = "Subjects", all = TRUE),
                            list(group_df, demo_covariate, outcome)) %>%
  arrange(Subjects) %>%
  mutate(Gender = as.factor(Gender),
         Subjects = as.factor(Subjects)) %>%
  drop_na(Dosage)

# Step 3: Define variables to impute for analysis
variables_to_impute <- c(
  "act-nonconscious-threat_vs_neutral-176064_Right_Amygdala",
  "act-nonconscious-threat_vs_neutral-911981_Right_sgACC",
  "ppi-nonconscious-threat_vs_neutral-911981_Right_sgACC-176064_Right_Amygdala"
)

# Initialize list to store results for each variable
results_list <- list()  
change_values_list <- list()

for (col in variables_to_impute) {
  
  # Prepare data for imputation
  data_forimpute_wide <- outcome_withgroup %>%
    select(Subjects, Group, Age, Gender, Dosage, all_of(col)) %>%
    pivot_wider(names_from = Dosage, values_from = all_of(col))
  
  # Initialize imputation without including Group as predictor
  micelong0 <- mice(data_forimpute_wide, maxit = 0)
  meth_micelong <- micelong0$method
  pred_micelong <- micelong0$predictorMatrix
  pred_micelong["Group", ] <- 0  # Exclude Group from being a predictor to avoid circularity
  pred_micelong["Age", ] <- 0
  pred_micelong["Gender", ] <- 0
  pred_micelong[, "Age"] <- 0
  pred_micelong[,"Gender"] <- 0
  pred_micelong["Subjects",] <- 0
  
  # Run multiple imputation
  imputed_data <- mice(data_forimpute_wide, meth = meth_micelong, pred = pred_micelong, maxit = 100, seed = 2019, printFlag = FALSE)
  
  # Fit linear mixed model on imputed data
  mods <- with(imputed_data, {
    dat_long <- pivot_longer(data_forimpute_wide, cols = -c(Subjects, Group, Age, Gender), names_to = 'Dosage', values_to = 'var') %>%
      merge(., outcome[, c("Subjects", "Dosage", "nonconscious_discarded_percent")], by = c("Subjects", "Dosage")) %>%
      filter(Dosage != 'Baseline' & Dosage != 'MDose')
    lmer('var ~ Dosage * Group +   Age + Gender + nonconscious_discarded_percent + (1 | Subjects)', data = dat_long, REML = FALSE)
  })


  # Pool and summarize results from imputed data
  pooled_results <- mice::pool(mods)
  fixed_effects_imputed <- summary(pooled_results, conf.int = TRUE) %>%
    mutate(Source = "Imputed", Variable = col) %>%
    filter(term == "Dosage1:Group1") %>%
    mutate(F_value = statistic^2) %>%
    mutate(
      `95% CI` = paste0("[", round(`2.5 %`, 2), ", ", round(`97.5 %`, 2), "]"),
      Variable = col
    ) %>%
    select(Variable, term, estimate, std.error, statistic, df, p.value, F_value, `95% CI`, Source)
  
  # Fit model on non-imputed data
  dat_long_no_impute <- pivot_longer(data_forimpute_wide, cols = -c(Subjects, Group, Age, Gender), names_to = 'Dosage', values_to = 'var') %>%
    merge(., outcome[, c("Subjects", "Dosage", "nonconscious_discarded_percent")], by = c("Subjects", "Dosage")) %>%
      filter(Dosage != 'Baseline' & Dosage != 'MDose')


  model_no_impute <- lmer('var ~ Dosage * Group + Age + Gender + nonconscious_discarded_percent + (1 | Subjects)', data = dat_long_no_impute, REML = FALSE)
  
  fixed_effects_no_impute <- broom.mixed::tidy(model_no_impute, effects = "fixed", conf.int = TRUE) %>%
    filter(term == "Dosage1:Group1") %>%
    mutate(F_value = statistic^2) %>%
    mutate(
      Source = "Non-imputed",
      `95% CI` = paste0("[", round(conf.low, 2), ", ", round(conf.high, 2), "]"),
      Variable = col
    ) %>%
    select(Variable, term, estimate, std.error, statistic, df, p.value, F_value, `95% CI`, Source)
  
  # Combine imputed and non-imputed results
  combined_results <- bind_rows(fixed_effects_no_impute, fixed_effects_imputed)
  results_list[[col]] <- combined_results
  
  
  # Calculate 120mg (HDose) minus placebo change for each imputed dataset
  change_results <- lapply(1:imputed_data$m, function(i) {
    imputed_data_complete <- complete(imputed_data, i)
    imputed_data_complete %>%
      mutate(change = HDose - Placebo) %>%  # Calculate 120mg - Placebo for the variable
      select(Subjects, Group, change) %>%
      rename(!!col := change)  # Rename column to indicate the variable
  })
  
  # Calculate the average change across imputations
  pooled_change <- bind_rows(change_results) %>%
    group_by(Subjects, Group) %>%
    summarize(across(everything(), mean, na.rm = TRUE), .groups = 'drop')
  
  # Store the results in change_values_list
  change_values_list[[col]] <- pooled_change
}

# Combine imputed and non-imputed results into a single data frame for viewing
final_results <- bind_rows(results_list) %>%
  mutate(across(c(estimate, std.error, statistic, df, p.value, F_value), round, 2))

# Display final results in table
final_results %>%
  kbl(caption = "Summary of statistical results with and without imputation") %>%
  kable_classic(full_width = F, html_font = "Arial", font_size = 10)

# Combine all (120mg - Placebo) change values into a single data frame for viewing
pooled_change_summary <- reduce(change_values_list, full_join, by = c("Subjects", "Group")) %>%
  arrange(as.numeric(Subjects))

# combine with non-brain (120mg - Placebo) change
change_from_placebo_to_120mg_long <- outcome_withgroup %>%
  filter(Dosage %in% c("Placebo", "HDose")) %>%
  select(Subjects, Group, Dosage, dgttrtAvN_norm, dascscore_impair, dascscore_anxiety, vas_bewithothers_post_pre, vas_secure_post_pre, faces1_4) %>%
  pivot_longer(cols = -c(Subjects, Group, Dosage), names_to = 'variables', values_to = 'value') %>%
  pivot_wider(names_from = Dosage, values_from = value) %>%
  mutate(change = `HDose` - Placebo) %>% # Calculate the change from Placebo to 120mg for each variable
  select(Subjects, Group, variables, change) %>%
  pivot_wider(names_from = variables, values_from = change, names_glue = "{variables}_change")

pooled_change_summary_all <- merge(pooled_change_summary, change_from_placebo_to_120mg_long, by = c("Subjects",'Group'), all = TRUE) %>%
  mutate(across(where(is.numeric), ~ round(., 2))) %>%
  arrange(as.numeric(Subjects))

# Display final change table in a clean format
pooled_change_summary_all %>%
  kbl(caption = "120mg minus Placebo Change for Each Participant Across Imputations") %>%
  kable_classic(full_width = F, html_font = "Arial", font_size = 10)

```


### calculate guess accuracies, including in high and low groups
### Suppl. Table 4
```{r fig.width=2,fig.height=2, fig.align='center',comment= NA, message=FALSE, tidy = TRUE, results='asis',warning=FALSE}
# Calculate accuracy of guesses for each type (CRC, Participant, MD)
correct_guess <- dosage_guesses %>%
  mutate(correct_CRC = case_when(CRC_guess == Dosage ~ 1, is.na(CRC_guess) ~ NA, TRUE ~ 0),
         correct_Participant = case_when(Participant_guess == Dosage ~ 1, is.na(Participant_guess) ~ NA, TRUE ~ 0),
         correct_MD = case_when(MD_guess == Dosage ~ 1, is.na(MD_guess) ~ NA, TRUE ~ 0))

# Summarize correct guesses by subject
summary_guess_subject <- correct_guess %>%
  group_by(Subjects) %>%
  summarise(correct_CRC_total = sum(correct_CRC, na.rm = TRUE),
            correct_Participant_total = sum(correct_Participant, na.rm = TRUE),
            correct_MD_total = sum(correct_MD, na.rm = TRUE),
            correct_CRC_percent = 100*correct_CRC_total/sum(!is.na(correct_CRC)),
            correct_Participant_percent = 100*correct_Participant_total/sum(!is.na(correct_Participant)),
            correct_MD_percent = 100*correct_MD_total/sum(!is.na(correct_MD)))

# Calculate average correct guess percentages across all subjects
summary_guess_average <- correct_guess %>%
  summarise(correct_CRC_total = sum(correct_CRC, na.rm = TRUE),
            correct_Participant_total = sum(correct_Participant, na.rm = TRUE),
            correct_MD_total = sum(correct_MD, na.rm = TRUE),
            correct_CRC_percent = 100*correct_CRC_total/sum(!is.na(correct_CRC)),
            correct_Participant_percent = 100*correct_Participant_total/sum(!is.na(correct_Participant)),
            correct_MD_percent = 100*correct_MD_total/sum(!is.na(correct_MD)))

# Calculate average correct guess percentages by dose
summary_guess_average_bydose <- correct_guess %>%
  group_by(Dosage) %>%
  summarise(correct_CRC_total = sum(correct_CRC, na.rm = TRUE),
            correct_Participant_total = sum(correct_Participant, na.rm = TRUE),
            correct_MD_total = sum(correct_MD, na.rm = TRUE),
            correct_CRC_percent = 100*correct_CRC_total/sum(!is.na(correct_CRC)),
            correct_Participant_percent = 100*correct_Participant_total/sum(!is.na(correct_Participant)),
            correct_MD_percent = 100*correct_MD_total/sum(!is.na(correct_MD)))

summary_guess_average_bydose %>%
  select(Dosage, correct_Participant_percent, correct_MD_percent, correct_CRC_percent) %>%
  t() %>%
kbl(caption = "Accurary of dosage identification across different conditions") %>%
kable_classic(full_width = F, html_font = "Arial", font_size = 10)


# Merge group information with correct guesses data
correct_guess_group <- Reduce(function(x, y) merge(x, y, by = c("Subjects"), all=TRUE), list(group_df,correct_guess))

# Calculate average correct guess percentages by dose and group
summary_guess_average_bydose_bygroup <- correct_guess_group %>%
  group_by(Dosage, Group) %>%
  summarise(correct_CRC_total = sum(correct_CRC, na.rm = TRUE),
            correct_Participant_total = sum(correct_Participant, na.rm = TRUE),
            correct_MD_total = sum(correct_MD, na.rm = TRUE),
            correct_CRC_percent = 100*correct_CRC_total/sum(!is.na(correct_CRC)),
            correct_Participant_percent = 100*correct_Participant_total/sum(!is.na(correct_Participant)),
            correct_MD_percent = 100*correct_MD_total/sum(!is.na(correct_MD)))

summary_guess_average_bydose_bygroup %>%
  select(Dosage, Group, correct_Participant_percent) %>%
  t() %>%
  kbl(caption = "Accurary of dosage identification across different conditions in high and low groups") %>%
  kable_classic(full_width = F, html_font = "Arial", font_size = 10)

```
